### 2016-10-03 Paper_Final.tex
Slight updates to scripts to renumber appendices to match paper.
Updated readme with better replication instructions.

\noindent\Large \textsc{Aaron Rudkin\footnote{I thank Natalie McNaught from the New Zealand Electoral Commission for her assistance securing and digitizing paper election records. My thanks also to Luke Sonnet, Adam Boche, Jeff Lewis, Michael F. Thies, and Kathy Bawn for input at various stages during this project. Any errors or omissions are my own. Replication data and code is available at: \textcolor{blue}{https://github.com/aaronrudkin/CabinetEffect}}}
\vspace*{0.1\textheight}

@@

\textmd{Although a long body of research has considered cabinet formation from the perspective of parties and coalitions, research on individual incentives to join cabinet has been limited thus far. Electoral benefits, which may stem from particularistic spending, differential credit claiming capacity, or party investment, provide one motivation to join cabinet. Martin (2016) uses Irish data to present evidence for electoral returns from cabinet membership. I extend Martin's analysis using a novel electoral dataset I constructed, examining Canada and New Zealand post-1945. In the Canadian data, I find a modest but substantively relevant positive effect, robust to alternate specifications and aggregations of the data. By contrast, the New Zealand data shows little to no effect. Limitations including endogeneity in cabinet selection, the observational nature of the data, limited biographical data, and the failure of the key result to replicate across institutional and cultural contexts suggest caution is warranted before drawing broader global conclusions.}

@@

\newpage
\section*{Appendix 2: Alternate Specifications, Canada}
\input{"Includes/appendix3"}

\newpage
\section*{Appendix 3: New Zealand Logit, Pre/Post MMP}
\input{"Includes/appendix4"}

>>>>

\noindent\Large \textsc{Aaron Rudkin\footnote{I thank Natalie McNaught from the New Zealand Electoral Commission for her assistance securing and digitizing paper election records. My thanks also to Kathy Bawn, Adam Boche, Jeff Lewis, Luke Sonnet, and Michael F. Thies for input at various stages during this project. Any errors or omissions are my own. Replication data and code is available at: \textcolor{blue}{https://github.com/aaronrudkin/CabinetEffect}}}
\vspace*{0.1\textheight}

@@

\textmd{Although a long body of research has considered cabinet formation from the perspective of parties and coalitions, research on individual incentives to join cabinet has been limited thus far. Electoral benefits, which may stem from particularistic spending, differential credit claiming capability, or party investment, provide one motivation to join cabinet. Martin (2016) uses Irish data to present evidence for electoral returns from cabinet membership. I extend Martin's analysis using a novel electoral dataset I constructed, examining Canada and New Zealand post-1945. In the Canadian data, I find a modest but substantively relevant positive effect, robust to alternate specifications and aggregations of the data. By contrast, the New Zealand data shows little to no effect. Limitations including endogeneity in cabinet selection, data limitations, and the failure of the key result to replicate across institutional and cultural contexts suggest caution is warranted before drawing broader global conclusions.}

@@

\newpage
\section*{Appendix 2: Alternate Specifications, Canada}
\input{"Includes/appendix2"}

\newpage
\section*{Appendix 3: New Zealand Logit, Pre/Post MMP}
\input{"Includes/appendix3"}
